%!TEX root = TTK4150-Summary.tex

\section{Definitions of stability}
\paragraph{Stability} The origin is stable iff
\begin{equation}
	\forall \quad \epsilon > 0 \quad \exists \quad \delta(\epsilon) > 0
	\mbox{ s.t. }
	||x(0)|| < \delta \implies ||x(t)|| < \epsilon \quad \forall \quad t \geq 0
\end{equation}

\section{Math}

\paragraph{Decrescentness}
$V(t,x)$ is \emph{decrescent} iff
\begin{equation}
	\begin{rcases}
		V(t,0) =    0      \\
		V(t,x) \leq W_2(x)
	\end{rcases}
	\forall \: t \geq 0
	\mbox{, for some pos. def. }
	W_2(x).
\end{equation}

\paragraph{Theorem 4.10}
If $\exists \: a, k_1, k_2, k_3 > 0$ such that
\begin{itemize}
	\item $V$ is $C^1$
	\item $k_1 ||x||^a \leq V(x) \leq k_2 ||x||^a \quad \forall \: x \in \mathbb{D}$
	\item $\dot{V}(x) \leq - k_3 ||x||^a \quad \forall \: x \in \mathbb{D}$
\end{itemize}
then the origin is \emph{exponentially stable}. If $\mathbb{D} = \mathbb{R}^n$, the origin is \emph{globally} exponentially stable.

\paragraph{Corollary 4.3}
The origin is ES iff $A$ is Hurwitz, with
\begin{equation}
	A =
	\begin{bmatrix}
		\pd{f}{x}
	\end{bmatrix}
	\evalat{x=0}
\end{equation}

\section{Lyapunov shit}

\subsection{Lyapunov function (LF)}
$V(x)$ is an LF iff
\begin{itemize}
	\item $V \in \mathbb{C}^1$
	\item $V(0) = 0$ \\
	      $V(x) > 0 \quad \forall \quad x \in \mathbb{D} \backslash \{0\}$
	\item $\dot{V}(0) = 0$ \\
	      $\dot{V}(x) \leq 0 \quad \forall \quad x \in \mathbb{D} \backslash \{0\}$
\end{itemize}

\subsection{Strict Lyapunov function (SLF)}
$V(x)$ is an SLF iff it is an LF and
\begin{itemize}
	\item $\dot{V}(x) < 0 \quad \forall \quad x \in \mathbb{D} \backslash \{0\}$
\end{itemize}

\section{Stability defined by Lyapunov functions}
\paragraph{Theorem 4.1 (Direct Lyapunov method)}
\begin{itemize}
	\item If $\exists$ an LF for the origin, then the origin is stable.
	\item If $\exists$ an SLF for the origin, then the origin is asymptotically stable.
\end{itemize}

\paragraph{Theorem 4.2}
If $\exists$ an SLF $V$ for the origin and $V$ is radially unbounded, then the origin is globally asymptotically stable.

\paragraph{Theorem 4.7 (Indirect Lyapunov method)}
Let $x=0$ be an equilibrium for $\dot{x} = f(x)$ where $f : \mathbb{D} \rightarrow \mathbb{R}^n$ satisfies $f \in \mathbb{C}^1$ and $\mathbb{D}$ is a neighborhood of the origin. Let
\begin{equation}
	A = \pd{f}{x} (x) \evalat{x=0}
\end{equation}

Then,
\begin{enumerate}
	\item The origin is asymp. stable if $\Re \lambda_i < 0$ for all eigenvalues of A.
	\item The origin is unstable if $\Re \lambda_i > 0$ for any eigenvalue of A.
\end{enumerate}

\paragraph{Theorem 4.4 (LaSalle's theorem)}
If $\exists V : \mathbb{D} \rightarrow \mathbb{R}$ such that
\begin{itemize}
	\item $V$ is $C^1$
	\item $\exists c > 0$ such that $\Omega_c = {x \in \mathbb{R}^n | V(x) \leq c} \in \mathbb{D}$ 
	\item $\dot{V}(x) \leq 0 \quad \forall \quad x \in \Omega_c$
\end{itemize}
